The impact of cosmic variance on simulating weak lensing surveys

### 2014-08-25 Writeup/paper_v2.tex
remove defunct comments

\begin{keywords}
 Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?}
\end{keywords}

\rachel{The title is overly vague.  I recommend something like ``The
  impact of cosmic variance on simulating weak lensing surveys''.}

\rachel{Also, a question: we had given up on using \sersicn{} or \btt{}
  because the distributions have a complicated form including edge
  effects, but did you ever try looking at a simple statistic like the
  mean value?  i.e., just like your plots of the RMS ellipticity
  vs. redshift with different color points for over/underdense
  regions, except that you would plot $\langle n_s \rangle$ or
  $\langle B/T\rangle$.}

\rachel{Finally, it seems that some of your figure files have not been
  committed to the repository, because I do not see them.  Also I
  cannot compile everything, because the figures are a mix of PDF, PNG, and EPS.
I need either EPS to compile using latex, or PDF and PNG to compile
using pdflatex.}

@@

\rachel{It's true that you should stress the importance of WL.  But
  I recommend restructuring this opening to be {\em constructive}
  rather than the current tone which is relatively negative.  To make
  it constructive, I suggest covering the following points in the
  following order:}
\begin{itemize}
\item Major surveys are planned in the next 1-2 decades
  to make measurements that will precisely constrain the nature of
  dark energy.
\item Weak lensing is one of the more important cosmological probes
  for this purpose.
\item For these upcoming surveys to achieve their promise, the
  systematic error budget must be below the statistical error budget.
  This means reducing systematic errors from their current typical
  level.
\item One method that is commonly used to test for the presence of
  systematics is image simulation.  Typically the most realistic ones
  use HST-based training samples based on COSMOS or the UDF, which are
  small areas of the sky.
\item THe goal of this work is to understand systematic uncertainties
  that might arise due to the finite size of these areas, when
  dividing the sample into redshift slices to test for shear
  systematics as a function of redshift.
\end{itemize}

\rachel{And then you can launch into some of your current text about why there
is cause for concern (known environment-morphology relations, etc.).}
\arun{Done.}

@@

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{fig4}
 \label{fig:comoving_densities}
 \caption{Differential comoving densities, integrated within a bin, are plotted. Red line refers to the average comoving density over the entire volume under consideration. 
          The green lines correspond to the 0.9 and 1.1 times the overall average.}
\end{figure}

@@

Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting. Refer to Figure~\ref{fig:comoving_densities}.
And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
%Refitting the model to our new sample is consistent with the previous assignment of overdensities.

@@

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
 \label{fig:comoving_densities}
 \caption{In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.}
\end{figure}

>>>>

\begin{keywords}
 Gravitational lensing: weak, Cosmology: Large-scale structure of Universe, Galaxies: evolution {\bf ?} \rachel{Are these from the MNRAS list?}
\end{keywords}

@@

@@

% \begin{figure}
%  \centering
%  \includegraphics[width=\columnwidth]{fig4}
%  \label{fig:comoving_densities}
%  \caption{Differential comoving densities, integrated within a bin, are plotted. Red line refers to the average comoving density over the entire volume under consideration. 
%           The green lines correspond to the 0.9 and 1.1 times the overall average.}
% \end{figure}

@@

Not surprisingly, we see the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density after volume limiting. %Refer to Figure~\ref{fig:comoving_densities}.
And the environmentally neutral regions fall below or at least lie close to the 10\% margin.
%Refitting the model to our new sample is consistent with the previous assignment of overdensities.

@@

% \begin{figure}
%  \centering
%  \includegraphics[width=\columnwidth]{../plots_20140219/comoving_densities(2b).png}
%  \label{fig:comoving_densities}
%  \caption{In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.}
% \end{figure}
